PM Mungbean meta-analysis

### 2021-03-09 02_Preliminary_analysis.Rmd
remove test code

# Obtain rainfall from bomrang

crop_rain(location_name = PM_MB_dat$location,
          latitude = PM_MB_dat$lat,
          longitude = PM_MB_dat$lon,
          first_day = PM_MB_dat$planting_date,
          last_day = PM_MB_dat$harvest_date)

PM_MB_dat$sum_rain <-
   crop_rain(location_name = PM_MB_dat$location,
          latitude = PM_MB_dat$lat,
          longitude = PM_MB_dat$lon,
          first_day = PM_MB_dat$planting_date,
          last_day = PM_MB_dat$harvest_date)

>>>>

# Obtain rainfall from bomrang
PM_MB_dat$sum_rain <-
   crop_rain(location_name = PM_MB_dat$location,
          latitude = PM_MB_dat$lat,
          longitude = PM_MB_dat$lon,
          first_day = PM_MB_dat$planting_date,
          last_day = PM_MB_dat$harvest_date)
